Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-30 paper/paper.tex
start related works

% Put the related works here
% \section{Related Works}

@@

This is a placeholder for a citation cos otherwise the compiler throws errors~\cite{AudioDistractionsAshley}.

>>>>

% Put the related works here
\section{Related Works}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. The other studies attempted to search for this answer by
focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, 
or determining if background music help users to keep their attention on their task at hand~\cite{kiss2021effect}.

@@
